### 2019-03-01 2019_csic5011/slides/homework02.tex
Add files via upload

The problem below marked by $^*$ is optional with bonus credits. % For the experimental problem, include the source codes which are runnable under standard settings.

@@

\url{http://math.stanford.edu/~yuany/course/ceph_hgdp_minor_code_XNA.txt.zip}

@@

\url{http://www.math.pku.edu.cn/teachers/yaoy/data/HGDP_region.mat}

>>>>

The problem below marked by $^*$ is optional with bonus credits. For the experimental problem, include the source codes which are runnable under standard settings. Since there is NO grader assigned for this class, homework will not be graded. But if you would like to submit your exercise, please send your homework to the address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com})  with a title ``CSIC5011: Homework \#". I'll read them and give you bonus credits.

@@

\url{https://www.dropbox.com/l/scl/AADN80paNFy1yB5gyYzNVOfkZGj9SiVDlZo}

@@

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/HGDP_region.mat}
